Abstract Plots

### 2021-07-22 Abstract.Rmd

#create vector of cosine similarities to the FFPE signature
ffpe.cosmic.cos.sims <- c()
for (i in 1:length(signature.names)){
  cos.sim <- cos_sim_matrix(signature.matrix.list[[i]], ffpe.signature)
  ffpe.cosmic.cos.sims[i] <- cos.sim[1,1]
}
```

>>>>

#create vector of cosine similarities to the FFPE signature
ffpe.cosmic.cos.sims <- c()
for (i in 1:length(signature.names)){
  cos.sim <- cos_sim_matrix(signature.matrix.list[[i]], ffpe.signature)
  ffpe.cosmic.cos.sims[i] <- cos.sim[1,1]
}

signature.4.mat <- as.matrix(cosmic.signatures[,"SBS4"])
rownames(signature.4.mat) <- mutations

signature.6.mat <- as.matrix(cosmic.signatures[,"SBS6"])
rownames(signature.6.mat) <- mutations
```

#Diagram of Methods

```{r}
mmr.sample <- create_signature_sample_vector(signature.6.mat, 200)
tobacco.sample <- create_signature_sample_vector(signature.4.mat, 200)
ffpe.sample <- create_signature_sample_vector(ffpe.signature, 100)

ex.ffpe.profile.mat <- vector_to_matrix(c(mmr.sample, tobacco.sample, ffpe.sample))
rownames(ex.ffpe.profile.mat) <- mutations

plot_96_profile(ex.ffpe.profile.mat)+
  labs(title = "Mutational Profile")
```

```{r}
sig.mat <- cbind(signature.4.mat, signature.6.mat, ffpe.signature)
colnames(sig.mat) <- c("Signature 4", "Signature 6", "FFPE")
fts.res <- fit_to_signatures(ex.ffpe.profile.mat, sig.mat)

plot_contribution(fts.res$contribution, sig.mat, coord_flip = TRUE)+
  labs(title = "Relative Contributions of Signatures")+
  theme(aspect.ratio = 0.3)
```

```{r}
plot_96_profile(sig.mat)+
  labs(title = "Mutational Signatures")
```

#Diagram of Simulating Data
```{r}
plot_96_profile(signature.4.mat)+
  labs(title = "Signature 4")
```

```{r}
plot_96_profile(ffpe.signature)+
  labs(title = "FFPE Signature")
```

```{r}
sample.4 <- create_signature_sample_vector(signature.4.mat, 100)
sample.ffpe <- create_signature_sample_vector(ffpe.signature, 100)

ex.sim.sample.vec <- c(sample.4, sample.ffpe)
ex.sim.sample <- vector_to_matrix(ex.sim.sample.vec)
plot_96_profile(ex.sim.sample)+
  labs(title = "Simulated Sample Profile")
```
